From Freebase to Wikidata: The Great Migration

### 2015-10-17 paper.tex
section 3.5.3, spoke about Figure 3

One such collaborative knowledge base is Freebase,
initially launched by Metaweb in 2007 and acquired by Google in 2010.
Another example is Wikidata, a~collaborative knowledge base developed by
Wikimedia Deutschland since 2012 and operated by the Wikimedia Foundation.
Due to the success of Wikidata, Google announced in 2014 to shut down Freebase and
help the community with the transfer of Freebase's content to Wikidata~\cite{freebase2014shutdown}.

@@

Freebase\footnote{Freebase: \url{https://www.freebase.com}} is an open and
collaborative knowledge base created in 2007 by Metaweb and 
acquired in 2010 by Google~\cite{freebase}.
It was used as the open core of the Google Knowledge Graph,
and has found many use cases outside of Google.
Due to the success of Wikidata,
Google announced in 2014 to close Freebase and offer most of its content to the
Wikidata community~\cite{freebase2014shutdown,freebase-end}.

@@

Thanks to these efforts, we have already mapped most of the topics that could be mapped automatically,
which is also backed by the comparably small increases gained from the ID reconciliation approach 
and the Knowledge Graph data described in the previous paragraph.
Furthermore, the \emph{mapped} topics have an average number of facts of about~13.9,
whereas the topics that were \emph{not} mapped have an average number of only 5.7~facts.
We have mapped the majority of all topics with more than 47~facts
(191K~non mapped topics \textit{vs.} 195K~mapped topics).
This allows us to conclude that we have mapped the most important items of Freebase.
\autoref{fig:mapped-not-mapped} provides an overview of mapped and non-mapped items
put in relation to the number of facts per item.
\todo{"There is no reference in the text to \autoref{fig:mapped-not-mapped}
(which has a lot of subtle information in it.) It needs some real explanation." -- Jamie}

>>>>

One such collaborative knowledge base is Freebase,
publicly launched by Metaweb in 2007 and acquired by Google in 2010.
Another example is Wikidata, a~collaborative knowledge base developed by
Wikimedia Deutschland since 2012 and operated by the Wikimedia Foundation.
Due to the success of Wikidata, Google announced in 2014 to shut down Freebase and
help the community with the transfer of Freebase's content to Wikidata~\cite{freebase2014shutdown}.

@@

Freebase\footnote{Freebase: \url{https://www.freebase.com}} is an open and
collaborative knowledge base publicly launched in 2007 by Metaweb and 
acquired in 2010 by Google~\cite{freebase}.
It was used as the open core of the Google Knowledge Graph,
and has found many use cases outside of Google.
Due to the success of Wikidata,
Google announced in 2014 to close Freebase and offer most of its content to the
Wikidata community~\cite{freebase2014shutdown,freebase-end}.

@@

Thanks to these efforts, we have already mapped most of the topics that could be mapped automatically,
which is also backed by the comparably small increases gained from the ID reconciliation approach 
and the Knowledge Graph data described in the previous paragraph.
This is no surprise, since the core of both projects was kickstarted by using
Wikipedia as a~repository of topics.

The \emph{mapped} topics have an average number of 13.9~facts,
whereas the topics that were \emph{not} mapped have an average number of only 5.7~facts.
We have mapped the majority of all topics with more than 47~facts
(191K~non mapped topics \textit{vs.} 195K~mapped topics).
This indicates that we have mapped the most important items of Freebase.
\autoref{fig:mapped-not-mapped} provides an overview of mapped and non-mapped items
put in relation to the number of facts per item: note that the Figure is log-scaled
on both axes, so the seemingly small area between the two lines covers a majority of
the topics. It can also be seen that there are a very small number of topics with
a high number of facts which have not been covered (in the lower part of the Figure).
These have all been manually inspected and found to be specific to the way knowledge
in Freebase is built. The vast majority of items with more than ten facts - in the
center of the Figure - has been mapped. The items that have not been mapped -
visible in the upper left corner of the image - are very thin,
i.e. mostly have a very small number of facts and
would not have added much to the knowledge base.
